Fixing Vulnerabilities Potentially Hinders Maintainability

### 2020-09-04 paper/emse20.tex
small fix

\textbf{Overall Score ($M(v)$):} 
Although overall patching vulnerabilities has a less negative impact
on software maintainability guidelines, this is not reflected in the 
average impact of all guidelines ($M(v)$) as we can see in 
Figure~\ref{fig:guidelines}. Remember that each point of the plot 
represents the impact of a security patch on software 
maintainability. Red, means the impact was negative, i.e., the patch 
harmed maintainability. Yellow, means the patch did not have any 
kind of impact on maintainability. Green, means the impact was 
positive, i.e., the patch improver software maintainability.
The $M(v)$ plot show that $406$ ($41.9\%$) cases have a negative 
impact on software maintainability. While $188$ ($19.4\%$) cases 
have no impact at all and $375$ ($38.7\%$) have a positive impact on 
software maintainability. The larger number of negative cases may be 
explained by guidelines with higher concentrations of negative 
cases with higher amplitudes, such as \emph{Write Short Units of 
Code}, \emph{Write Simple Units of Code} and \emph{Separate Concerns 
in Modules}---more red points on the left, being $0$ the middle.

@@

\textbf{Summary:} Security-related commits are expected to harm software 
maintainability. In contrast, one cannot say the same about
regular changes, in which \textbf{no significant differences are observed}. 
Thus, we urge the importance of adopting maintainability practices while 
applying security patches.

>>>>

\textbf{Overall Score ($M(v)$):} 
Although overall patching vulnerabilities has a less negative impact
on software maintainability guidelines, this is not reflected in the 
average impact of all guidelines ($M(v)$) as we can see in 
Figure~\ref{fig:guidelines}. Remember that each point of the plot 
represents the impact of a security patch on software 
maintainability. Red, means the impact was negative, i.e., the patch 
harmed maintainability. Yellow, means the patch did not have any 
kind of impact on maintainability. Green, means the impact was 
positive, i.e., the patch improver software maintainability.
The $M(v)$ plot show that $406$ ($41.9\%$) cases have a negative 
impact on software maintainability. While $188$ ($19.4\%$) cases 
have no impact at all and $375$ ($38.7\%$) have a positive impact on 
software maintainability. The larger number of negative cases may be 
explained by guidelines with higher concentrations of negative 
cases with higher amplitudes, such as \emph{Write Short Units of 
Code}, \emph{Write Simple Units of Code} and \emph{Separate Concerns 
in Modules}---more red points on the left, being $0$ the reference point.

@@

\textbf{Summary:} Security-related commits are observed to harm software 
maintainability. In contrast, one cannot say the same about
regular changes, in which \textbf{no significant differences are observed}. 
Thus, we urge the importance of adopting maintainability practices while 
applying security patches.
